### 2024-01-09 documentation/thesis/thesis_document.tex
more thesis

An overview of these is given in the subchapters as the following. There
are also introductory examples which provide an overview of the basic
functions in the \passthrough{\lstinline!Examples!}\ref{examples}
section, as well as further examples in the online documentation.
\cite{MagneticReadoutProcessingReadTheDocs}

@@

@@

@@

\hypertarget{storage-and-datamanagement}{%
\section{Storage and Datamanagement}\label{storage-and-datamanagement}}

\begin{lstlisting}[caption={JSON export structure of an MRPReading based measurement}, label=lst:json_export_format_example]
{
  "time_start": "Wed Sep 20 08:50:13 2023",
  "time_end": "Wed Sep 20 08:50:13 2023",
  "additional_data": {
      "sensor_device_path": "/dev/cu.usbmodem3867315334391",
      "sensor_name": "Unified Sensor Single Sensor",
      "sensor_id": "386731533439",
      "sensor_capabilities": ["static", "axis_b", "axis_x", "axis_y", "axis_z", "axis_temp", "axis_stimestamp"],
      "configname": "calibrationtemp30.yaml",
      "runner": "cli"
  },
  "data": [{
      "value": 0.135,
      "is_valid": true,
      "id": 0,
      "temperature": 34.32
  }],
  "measurement_config": {
      "id": "525771256544952",
      "sensor_distance_radius": 40.0,
      "magnet_type": 0
  },
  "name": "calibrationtemp30",
}
\end{lstlisting}

>>>>

An overview of these is given in the subchapters as the following. There
are also introductory examples which provide an overview of the basic
functions in the \passthrough{\lstinline!Examples!}\ref{examples}
section, as well as further examples in the online
documentation\cite{MagneticReadoutProcessingReadTheDocs}.

@@

The included core modules are essential for using the library. Basic
data types are implemented, as well as functions for import and export.
In addition, there are other support scripts that are required
internally.

The following modules are implemented in detail:

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!MRPReading!} - storage of measured values
\item
  \passthrough{\lstinline!MRPMeasurementConfig!} - storage of the
  measurement parameters
\item
  \passthrough{\lstinline!MRPMagnetTypes!} - various physical constants
  for basic magnet types
\end{itemize}

The \passthrough{\lstinline!MRPReading!} module performs a crucial role
in streamlining the centralized management of measurement data. It
serves as a storage provider for various measurements, offering
functionalities that facilitate the creation and addition of data
records. To customize and add meta-data, users have the flexibility to
configure parameters through the dedicated
\passthrough{\lstinline!MRPMeasurementConfig!} module into an
\passthrough{\lstinline!MRPReading!} instance.

Within the realm of measurement data, a diverse range of data points can
be seamlessly incorporated. The process is initiated by employing
specialized functions designed for the creation and addition of data
records. To configure parameters, ensuring a tailored approach to the
entire measurement process, these parameters act as a crucial bridge
between user preferences and the robust capabilities of the
\passthrough{\lstinline!MRPReading!} module.

The system is also designed to be compatible with
\passthrough{\lstinline!Extension Modules!}\ref{extension-modules},
allowing the generation of measurement data through various modules.
This extensibility enhances the versatility of the system, accommodating
diverse measurement scenarios and expanding its utility across different
domains.

To enhance the accessibility and interpretability of the recorded data,
a dedicated module, MRPMagnetTypes, comes into play. This module is
specifically designed for the storage of physical parameters pertaining
to the magnets targeted for measurement. By centralizing this
information, users can streamline the subsequent phases of evaluation
and analysis, simplifying the overall process and ensuring a more
efficient and insightful exploration of the collected data.

At the end of processing, the collected data is typically exported;
various functions are provided for this purpose. These are described as
the following.

\hypertarget{storage-and-datamanagement}{%
\subsubsection{Storage and
Datamanagement}\label{storage-and-datamanagement}}

\begin{lstlisting}[caption={JSON export structure of an MRPReading based measurement}, label=lst:json_export_format_example]
{
  "time_start": "Wed Sep 20 08:50:13 2023",
  "time_end": "Wed Sep 20 08:54:13 2023",
  "additional_data": {
      "sensor_device_path": "/dev/cu.usbmodem3867315334391",
      "sensor_name": "Unified Sensor Single Sensor",
      "sensor_id": "386731533439",
      "sensor_capabilities": ["static", "axis_b", "axis_x", "axis_y", "axis_z", "axis_temp", "axis_stimestamp"],
      "configname": "calibrationtemp30.yaml",
      "runner": "cli"
  },
  "data": [{
      "value": 0.135,
      "is_valid": true,
      "id": 0,
      "temperature": 34.32
  }],
  "measurement_config": {
      "id": "525771256544952",
      "sensor_distance_radius": 40.0,
      "magnet_type": 0
  },
  "name": "calibrationtemp30",
}
\end{lstlisting}

@@

In order to give the user the possibility to display the recorded data
visually, two modules were created, which can graphically prepare
\passthrough{\lstinline!MRPReading!} instances:

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!MRPVisualization!} - different table, graph
  based plots
\item
  \passthrough{\lstinline!MRPPolarVisualization!} - fullsphere map plots
\end{itemize}

On the one hand, it is possible with the
\passthrough{\lstinline!MRPVisualization!} module to display measurement
data as a table or streamplot, lineplot. This makes it possible, for
example, to visually identify outliers or trends in the measurement
data. These can also be saved as an image file. The module is compatible
with all measurement data.

In contrast to the \passthrough{\lstinline!MRPPolarVisualization!}
module, this provides functions to create 2D map plots in the polar
coordinate system. This requires measurement data with additionally set
spatial coordinates. These can be generated automatically with the
\passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere} sensor, or
the user must provide the spatial information from another source.

@@
